D.I.A.G.R.A.M.: Development of Image Analysis for Graph Recognition And Modeling

### 2025-06-29 doc/article/article.tex
Updated paper

\section{Related Works}
\cite{arrowrcnn} \\
\cite{interactiveUML} \\
\cite{sketchdiagram}

>>>>

\section{Related Works}
The area of analyzing handwritten diagrams has been already studied in literature. Some key, modern, contributions are highlighted in this section.

Various works have already focused on the development, training and evaluation of specific deep-learning networks for extracting structures in arrow-oriented diagrams (like \textbf{Arrow R-CNN} \cite{arrowrcnn}). More traditional approaches tipically focus on specific diagram types and a restricted set of elements in them (e.g., \textbf{UML} \cite{interactiveUML}).

Some works in certain elements recognition - like arrows - are particularly domain-specific (like medical imaging \cite{med1}\cite{med2}). Other studies focus on the so-called \textit{online recognition} task, whose goal is to recognize diagrams as they are drawn (see \cite{online1}, \cite{online2}) - which could employ 'relative' strokes.
\cite{sketchdiagram}
